---
title: "gameday"
author: "Zichun Ye"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

You know then problem: You're in your office writing R code and suddenly have 
the urge to check whether your NHL team has a game or what the scores of NHL 
games are today. Before you know it you just wasted 15 minutes browsing the 
lastest news on your favorite hockey webpage. Suffer no more! You can now ask 
R directly, without tempting yourself by firing up your web browser.

## Function


1. `gday`
   - parameter: `team` and `date`;
   - return: Logical. `TRUE` if `team` has a NHL game on `date`, `FALSE` otherwise.
  
2. `scores`
   - parameter: `date`;
   - return: a date frame with game place, home team, away team, home score, away score and whether the game is completed.
  
3. `info_team`
   - parameter: `team` and `date`;
   - return: a date frame with information about arean, team, lat and long
  
## Dataset

arena_team: information about arean, team, lat and long



## More Examples

The following is some examples of these two functions.


* E.g. 1: calculate the winning percentage of home team in the past month.
```{r, results='asis'}
library(plyr)
library(ggplot2)
library(ggthemes)
library(gameday)
date<-data.frame(date = as.Date(-30:0,Sys.time()))

perc<-ddply(date, ~date, function(x){
	score<-scores(x$date)
	return(data.frame(perc=nrow(score[score$home_score>score$away_score,])/nrow(score)))
})

ggplot(perc,aes(x = date, y = perc))+
	geom_point()+
	geom_smooth(method = "loess")+
	theme_gdocs()
```

* E.g. 2: compare games and back to back games of Canucks in the last 6 weeks.

Here back to back game is defined to be have games in two contiguous days.
```{r, results='asis'}
date<-data.frame(date = as.Date(-41:0,Sys.time()))

games<-ddply(date, ~date, function(x){
	if(gday(date = x$date)) return(TRUE)
	return(FALSE)
})
backtoback<-ddply(date, ~date, function(x){
	if(gday(date = x$date)&gday(date = x$date+1)) return(TRUE)
	return(FALSE)
})

data<-data.frame(week = 1:6)

for(i in 1:6){
	data$game[i] = sum(games[(7*i-6):(7*i),2])
	data$backtoback[i] = (sum(backtoback[(7*i-6):(7*i),2])!=0)
}


ggplot(data, aes(week,game,fill=backtoback))+
  geom_bar(stat="identity")+
  theme_gdocs()	
```

The red bar represents the week without back to back game while the green one represent the week with back to back games.
