---
title: "gameday"
author: "Zichun Ye"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

You know then problem: You're in your office writing R code and suddenly have 
the urge to check whether your NHL team has a game or what the scores of NHL 
games are today. Before you know it you just wasted 15 minutes browsing the 
lastest news on your favorite hockey webpage. Suffer no more! You can now ask 
R directly, without tempting yourself by firing up your web browser.

## Function

* `gday`
  - parameter: `team` and `date`;
  - return: Logical. `TRUE` if `team` has a NHL game on `date`, `FALSE` otherwise.
* `scores`
  - parameter: `date`;
  - return: a date frame with home team, away team, home score and away score.


## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
